Computational methods in landscape ecology

### 2024-10-18 Sections/01-introduction.qmd
adds tiny improvements to the intro

<!-- R1: Very good idea to suggest software implementing methodological developments. It would be even better with a recapitulative table -->
Here, we introduce recent computational developments in multiple key topics of landscape ecology (Fig. 1), including software that implements or is potentially capable of implementing them (Tab. 1).
In this context, we are focusing on open-source software and scripting languages such as R, Python, and Julia.
However, we do not provide a systematic literature review or a general introduction to (computational) landscape ecology.
For such, please see @Turner2015LandscapeEcology, @Gergel2017LearningLandscape, or @With2019EssentialsLandscape.

@@

![Overview of landscape ecology topics for which computational methods are discussed. Contains modified Copernicus Sentinel data 2024-09-07 for Sentinel data.](Figures/Fig-1.jpg)

>>>>

<!-- R1: Very good idea to suggest software implementing methodological developments. It would be even better with a recapitulative table -->
Here, we introduce recent computational developments in multiple key topics of landscape ecology (Fig. 1), including software that implements or is potentially capable of executing them (Tab. 1).
In this context, we are focusing on open-source software and scripting languages such as R, Python, and Julia.
However, we do not provide a systematic literature review or a general introduction to (computational) landscape ecology.
For such, please see @Turner2015LandscapeEcology, @Gergel2017LearningLandscape, or @With2019EssentialsLandscape.

@@

![Overview of landscape ecology topics for which computational methods are discussed. The image uses modified Copernicus Sentinel-2 data from 2024-09-07.](Figures/Fig-1.jpg)
